%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Consultant} % Job title
    {OPITZ Consulting Deutschland GmbH} % Organization
    {Hamburg, Germany} % Location
    {Oct. 2016 - PRESENT} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
    {Danggeun Pay Inc. (KarrotPay)} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2021 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Tackling the challenges of digitalization with our customers.}
        \item{Tacking responsibility for the success of our solutions.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Risk Instruments\& Intern Business Intelligence} % Job title
    {Mercedes Benz Financial Services Japan AG} % Organization
    {Tokyo, Japan} % Location
    {Sep. 2014 - Apr. 2015} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Founding Member \& Director of Infrastructure Division} % Job title
    {Kasa} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2018 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Implementing reporting solutions to improve manual processes and shorten the monthly reporting time from three days to thirty minutes.}
        \item{Planning and implementation of an OLAP-Cube to enable analysts to query the information they need for their job in order to answer the question they had about their business and not only run fixed, static reports.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {Software Engineer \& Research Assistant} % Job title
    {Eudemonia Solutions AG} % Organization
    {Magdeburg, Germany} % Location
    {Jun. 2016 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developing Software in Scrum teams to react as quick as possible to changing priorities.}
        \item{Planning and implementing reporting solutions to support our customer to focus on their job and not on gathering data manually.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
