%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Multiple Positions, currently Lead Consultant - part time} % Job title
    {OPITZ CONSULTING GmbH} % Organization
    {Hamburg, Germany} % Location
    {Oct. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems}
        \item {DevOps Teamlead with currently 11 Engineers and more than 20 customers}
        \item {Technical customer lead for multiple public cloud customers. Mostly AZURE, AWS and GCP.}
        \item {Software Development for multiple German customers}
        \item {Building up a 24/7 support infrastructure for the largest german steel producer.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{SAP Consultant} % Job title
{mindsquare GmbH} % Organization
{Bielefeld, Germany} % Location
{Apr. 2015 - Oct. 2016} % Date(s)
{
  \begin{cvitems}
    \item {ABAP Development for different clients. }
    \item {Teamlead for a group of trainees. }
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Risk Instruments\& Intern Business Intelligence} % Job title
    {Mercedes Benz Financial Services Japan AG} % Organization
    {Tokyo, Japan} % Location
    {Sep. 2014 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Providing new ad-hoc reporting solutions for business analysts.}
        \item {Designing and implementing a data warehouse for the Japanese market.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer \& Research Assistant} % Job title
    {Eudemonia Solutions AG} % Organization
    {Magdeburg, Germany} % Location
    {Oct. 2010 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Software Development for financial institutions.}
        \item{Designing and implementing reporting solutions}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
